Simulations

### 2018-04-26 3-simus.Rmd
add biglasso comparison

```{r, message=FALSE}
library(tidyverse)
library(glue)
```

@@

    # GWAS
    gwas.train <- big_univLogReg(
      G, pheno.all[ind.train], ind.train = ind.train, 
      covar.train = covar.all[ind.train, , drop = FALSE], 
      ncores = nb_cores()
    )
    gwas.train.gc <- snp_gc(gwas.train)

    # Clumping on the test set
    ind.keep <- snp_clumping(G, infos.chr = infos.chr,
                             ind.row = ind.test,
                             thr.r2 = 0.2, 
                             S = abs(gwas.train.gc$score),
                             size = 500,
                             is.size.in.bp = TRUE,
                             infos.pos = infos.pos,
                             ncores = nb_cores())

@@

    cmsa.logit <- big_spLogReg(X = G, y01.train = pheno.all[ind.train], 
                               ind.train = ind.train, 
                               covar.train = covar.all[ind.train, , drop = FALSE],
                               ncores = nb_cores())

@@

    biglasso <- biglasso(G3, pheno.all, ind.train, ncores = nb_cores(),
                         penalty = "enet", family = "binomial", alpha = 0.5)

>>>>

```{r, message=FALSE}
library(tidyverse)
library(glue)
NCORES <- 6
```

@@

    # GWAS
    gwas.train <- big_univLogReg(
      G, pheno.all[ind.train], ind.train = ind.train, 
      covar.train = covar.all[ind.train, , drop = FALSE], 
      ncores = NCORES
    )
    gwas.train.gc <- snp_gc(gwas.train)

    # Clumping on the test set
    ind.keep <- snp_clumping(G, infos.chr = infos.chr,
                             ind.row = ind.test,
                             thr.r2 = 0.2, 
                             S = abs(gwas.train.gc$score),
                             size = 500,
                             is.size.in.bp = TRUE,
                             infos.pos = infos.pos,
                             ncores = NCORES)

@@

    cmsa.logit <- big_spLogReg(X = G, y01.train = pheno.all[ind.train], 
                               ind.train = ind.train, 
                               covar.train = covar.all[ind.train, , drop = FALSE],
                               ncores = NCORES)

@@

    biglasso <- biglasso(G3, pheno.all, ind.train, ncores = NCORES,
                         penalty = "enet", family = "binomial", alpha = 0.5)
